Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-04-27 ltx/data_paper/DataPaper.tex
added second derivative test for maximisation step in data paper

hence \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum. Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}. \blue{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativetheta} and \eqref{eq:SecondDerivativedisturbance}, disturbance estimates clearly represent maxima of the $\mathcal{Q}$-function.

>>>>

meaning \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum. Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}. \blue{don't know how to prove $q$ is of rank $n_{\theta}$} According to \eqref{eq:SecondDerivativetheta} and \eqref{eq:SecondDerivativedisturbance}, disturbance and noise estimates clearly represent maxima of the $\mathcal{Q}$-function.
